Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-20 paper/current/main.tex
Another small change in main text
added new SI text section

It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.

@@

%
%
\paragraph*{S1 Text}
\label{si:text:mobility_science}
{\bf Mobility and science.}
TODO: why is mobility important to science?

@@

For example, a researcher listing the set of affiliations $\{A, B, C\}$ on papers published in three different years will be considered two distinct instances of mobility, ${A \leftrightarrow B}$ and ${B \leftrightarrow C}$, where ${A \leftrightarrow B} = {B \leftrightarrow A}$ and  ${B \leftrightarrow C} = {C \leftrightarrow B}$.

>>>>

Here, we propose a neural embedding model as an efficient means of encoding an effective measure of distance using large-scale data on mobility trajectories, one that encodes complex latent structure.
It has been demonstrated that the neural embedding model preserves semantic relationships between words in a dense, continuous and meaningful low-dimensional vector representation~\autocite{mikolov2013word2vec}, and has been applied to reveal insights in text~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic}, documents~\autocite{le2014doc2vec, nakandala2016twitch}, and networks~\autocite{perozzi2014deepwalk, grover2016node2vec}.
In addition to encoding latent structure, this approach is computationally efficient, scalable for large datasets, robust to noise, and allows for a range of unique analyses that leverage their semantic properties using simple vector arithmetic.

@@

%
%
\paragraph*{S1 Text}
\label{si:text:mobility_science}
{\bf Mobility and science.}

Mobility is essential to the scientific enterprise.

@@

We adopt a data-driven approach to constructing mobility trajectories, making as little adjustment to the raw bibliometric data as possible. 
For each mobile researcher (having at least two distinct affiliations), we construct a mobility trajectory based on the affiliations listed on their published papers indexed in the Web of Science database between 2008 and 2019. 
An author is considered mobile if they published with at least two distinct affiliations during the time period of study. 
Affiliations map to disambiguated organizations, each of which matches to a unique identifier. 
Affiliations in a trajectory are first ordered by year of publication.
For example, if an author published with affiliation $A$ in $t_{0}$, affiliation $B$ in $t_{1}$, and $A$ again in $t_{2}$, then their ordered mobility trajectory would be $\{A, B, C\}$.

In the case that multiple affiliations are used within a single year, affiliations listed on publications published in that year are shuffled between each stage of the \textit{word2vec} training process (each epoch). 
For example, an author who published with affiliation $A$ in $t_{0}$, and affiliations $B, C$ in $t_{1}$ could appear as one of $\{A, B, C\}$ or $\{A, C, B\}$ in each training iteration. 
This effectively removes the effect of order within a year, as order cannot be meaningfully established based on co-affiliations in a single paper, or on different affiliations listed on separate papers, publication of which is not necessarily representative of the actual completion of the project.

Other than restricting to only mobile researchers, we do not perform any filtering or reductions to mobility trajectories.
For example, in the case than an author publishes with organization $A$ four times in $t_{0}$, and affiliation $B$ two times in $t_{1}$, then their trajectory will be $\{A, A, A, A, B, B\}$. 
This means that mobile authors who publish more papers will have longer trajectories.
However, \textit{word2vec} will skip duplicate consecutive organization IDs, effectively eliminating the impact of these long repetitive trajectories.
